### 2022-06-13 paper.tex
clarify caption

\begin{figure*}
    \begin{center}
    A\hspace{.4\textwidth}B\hspace*{.3\textwidth}~\\
    \hspace{.3cm}\includegraphics[width=.35\textwidth]{part_leonie_git/leonie_plots/complete_135k_12cm_log.pdf}
    \hspace{1cm}\includegraphics[width=.35\textwidth]{part_leonie_git/leonie_plots/cell500_20k_12cm_log.pdf}\\
    C\hspace*{.7\textwidth}~\\
    \hspace{.3cm}\includegraphics[width=.75\textwidth]{part_leonie_git/leonie_plots/UMAP_fulldataset.pdf}\\
    D\hspace*{.7\textwidth}~\\
    \hspace{.3cm}\includegraphics[width=.75\textwidth]{part_leonie_git/leonie_plots/UMAP_reduceddataset.pdf}
    \caption{\small \textbf{Benchmark of our methods on single-cell methylomes of 16 neuronal subtypes}. \textbf{(A)} Nearest neighbor count score using four different method combinations and a variable number of genomic intervals (regions) as input to PCA. Exemplary UMAPs for encircled analyses are shown in (C). \textbf{(B)} Same benchmark as in (A), but for a smaller data set consisting of 500 randomly subsampled cells. Exemplary UMAPs for analyses are shown in (D). \textbf{(C)} Two exemplary UMAPs of the full data set and methylation fractions of 100~kb windows (left) or shrunken residuals of variable methylation intervals (right) \textbf{(D)} Two exemplary UMAPs of the smaller data set and methylation fraction of 100~kb windows (left) or shrunken residuals of variable methylation intervals (right). Data from \citet{luo2017single}.}
    \label{figure:score}
    \end{center}
\end{figure*}

>>>>

\begin{figure*}
    \begin{center}
    A\hspace{.4\textwidth}B\hspace*{.3\textwidth}~\\
    \hspace{.3cm}\includegraphics[width=.35\textwidth]{part_leonie_git/leonie_plots/complete_135k_12cm_log.pdf}
    \hspace{1cm}\includegraphics[width=.35\textwidth]{part_leonie_git/leonie_plots/cell500_20k_12cm_log.pdf}\\
    C\hspace*{.7\textwidth}~\\
    \hspace{.3cm}\includegraphics[width=.75\textwidth]{part_leonie_git/leonie_plots/UMAP_fulldataset.pdf}\\
    D\hspace*{.7\textwidth}~\\
    \hspace{.3cm}\includegraphics[width=.75\textwidth]{part_leonie_git/leonie_plots/UMAP_reduceddataset.pdf}
    \caption{\small \textbf{Benchmark of our methods on single-cell methylomes of 16 neuronal subtypes}. \textbf{(A)} Nearest neighbor count score using four different method combinations and a variable number of genomic regions (VMRs or 100~kb windows) as input to PCA. Exemplary UMAPs for encircled analyses are shown in (C). \textbf{(B)} Same benchmark as in (A), but for a smaller data set consisting of 500 randomly subsampled cells. Exemplary UMAPs for analyses are shown in (D). \textbf{(C)} Two exemplary UMAPs of the full data set and methylation fractions of 100~kb windows (left) or mean shrunken residuals of VMRs (right) \textbf{(D)} Two exemplary UMAPs of the smaller data set and methylation fraction of 100~kb windows (left) or mean shrunken residuals of VMRs (right). Data from \citet{luo2017single}.}
    \label{figure:score}
    \end{center}
\end{figure*}
